On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-16 2_bg.tex
Spell check'd

\textcolor{red}{ This paper is a revised and extended version of
research that appeared at SIGIR 2015~\cite{ME-SIGIR15}.
In particular, this version adds: a new research question of whether
crowdsourcing is a viable method to gather robust magnitude estimation
values (RQ2); related background on crowdsourcing; more information on
the ME score distributions reported in Section~\ref{sec:descr-stat},
including Figures~\ref{fig:ME-raw-scores} and~\ref{fig:ME-norm-scores}
and their discussion; a new Section~\ref{sec:cs} including
Figure~\ref{fig:judgeVariability} and recomputation of
Figure~\ref{fig:workersQuality}; new material in Section~\ref{sec:rq2},
including recomputation of Figures~\ref{fig:runs-rerank-median3best}
and~\ref{fig:runs-rerank-median3best-fake}; a revised second half of
Section~\ref{sec-rq3}; an Appendix giving exact participant
instructions; and additional references.
}

>>>>

\textcolor{red}{ This paper is a revised and extended version of
research that appeared at SIGIR 2015~\cite{ME-SIGIR15}.
In particular, this version adds: a new research question of whether
crowdsourcing is a viable method to gather robust magnitude estimation
values (RQ2); related background on crowdsourcing; more information on
the ME score distributions reported in Section~\ref{sec:descr-stat},
including Figures~\ref{fig:ME-raw-scores} and~\ref{fig:ME-norm-scores}
and their discussion; a new Section~\ref{sec:cs} including
Figure~\ref{fig:judgeVariability} and re-computation of
Figure~\ref{fig:workersQuality}; new material in Section~\ref{sec:rq2},
including re-computation of Figures~\ref{fig:runs-rerank-median3best}
and~\ref{fig:runs-rerank-median3best-fake}; a revised second half of
Section~\ref{sec-rq3}; an Appendix giving exact participant
instructions; and additional references.
}

### 2016-09-16 6_results_RQ2.tex
Spell check'd

\textcolor{red}{ 
Using ME with crowdsourcing could potentially raise
several concerns, including: 
subjectiveness of the relevance scale; 
difficulty in normalizing disparate scales from different workers; 
lack of proper training of workers;
potential internal and/or external disagreement between workers;
and high overall cost as redundant workers needed to ensure quality.
On the basis of the results presented so far we can conclude that, at
least with our setting and our quality checks in place (see items
(a)--(d) in Section~\ref{sec:quality-checks}), we can be reassured that
magnitude estimation relevance scores gathered by means of
crowdsourcing are reliable, thus answering RQ\ref{item:rq4}.
Also, the cost to collect the ME judgements in our experiments 
is comparable to that of collecting ordinal scale judgements, 
and there are hints that this cost can be lowered by collecting fewer judgments.
}

>>>>

\textcolor{red}{ 
Using ME with crowdsourcing could potentially raise
several concerns, including: 
subjectiveness of the relevance scale; 
difficulty in normalizing disparate scales from different workers; 
lack of proper training of workers;
potential internal and/or external disagreement between workers;
and high overall cost as redundant workers needed to ensure quality.
On the basis of the results presented so far we can conclude that, at
least with our setting and our quality checks in place (see items
(a)--(d) in Section~\ref{sec:quality-checks}), we can be reassured that
magnitude estimation relevance scores gathered by means of
crowdsourcing are reliable, thus answering RQ\ref{item:rq4}.
Also, the cost to collect the ME judgments in our experiments 
is comparable to that of collecting ordinal scale judgments, 
and there are hints that this cost can be lowered by collecting fewer judgments.
}

### 2016-09-16 7_results_RQ3.tex
Spell check'd

Given that the agreement between our magnitude scores, TREC judgments
and Sormunen's judgments is not perfect, it is reasonable to expect
that relative system effectiveness orderings computed with each of
these as a basis may differ.
We first examine the correlation between system orderings using
magnitude estimation scores and TREC relevance as gain values, as for
both these judgment sets we have nearly complete coverage of the top 10
documents of all runs submitted to TREC-8, for our 18 judged topics.
% In the conference version of this paper~\cite{ME-SIGIR15} we showed the
% system scores (mean over all 18 topics) using median magnitude
% estimation scores per document (x-axis), and binary TREC categories
% (y-axis).
% This gave a result similar to Figure~\ref{fig:runs-rerank-median3best}.
% Unjudged documents were assumed to be irrelevant, as is common practice
% when using TREC data.
% \aht{What do you think of this almost self-referential style?}
% 
% Here we make a small alteration to the aggregation of the ME scores to
% get a single score for a document.
Rather than taking the median of all scores assigned to a document, we
take the median of scores taken from the three units that have document
orderings that have the highest agreement with the TREC orderings, or
Sormunen orderings, respectively.
In effect, the scores derived from units with high internal agreement as
computed in Section~\ref{sec:internal-agreement}, with ties broken in favor
of units with the least unjudged documents.
By aggregating scores over units that have a high agreement with the
original TREC orderings, any differences in system rankings we see should be more
attributable to the scale of the gain values, rather than perturbations in
document orderings given by different gain values.
\textcolor{red}{Note that this is a slightly less confounded methodology 
than was used in our previous paper~\cite{ME-SIGIR15}, which simply took the median 
of all units, even if the unit wildly disagreed with the ordering of documents
given by the categorical judgements. This revised methodology accounts for the 
differences between the figures and tables in this section and 
in the previous paper.}

@@

\textcolor{red}{
Generally the correlations between the system rankings based on 
categorical and ME gain values are higher when the wide judgements
are used as opposed to the narrow judgements.
This contradicts our expectations from 
Table~\ref{tab:scaling-cats}, which indicated that
a larger scale of gains led to a decrease in correlations.
This confirms that a simple argument based on the scale 
of judgements is not sufficient in explaining different system orders, 
although the number of topics used here is small (12).
We examine this further in the next section.
}

@@

\textcolor{red}{ In answering RQ\ref{item:rq2}, we have shown that
there are clear differences in system rankings using nDCG and ERR
metrics on this data when using ME scores as gain values compared with
using ordinal categories as gain values.
Depending on the judgements and the metric used, correlations between
system orderings using ME and the categorical judgements, as measured
with Kendall's $\tau$, varied between about 0.8 and -0.2. At first this
might seem like a simple scaling problem, where ME judgements are over
a wider range than categorical judgments.
However, analysis shows that simple factor cannot be the whole answer;
a much more likely explanation is that there is substantial individual
variance in not only how people perceive the relevance of an individual
document, but also in how they perceive the ratio of relevance of one
document to another.
}

>>>>

Given that the agreement between our magnitude scores, TREC judgments
and Sormunen's judgments is not perfect, it is reasonable to expect
that relative system effectiveness orderings computed with each of
these as a basis may differ.
We first examine the correlation between system orderings using
magnitude estimation scores and TREC relevance as gain values, as for
both these judgment sets we have nearly complete coverage of the top 10
documents of all runs submitted to TREC-8, for our 18 judged topics.
% In the conference version of this paper~\cite{ME-SIGIR15} we showed the
% system scores (mean over all 18 topics) using median magnitude
% estimation scores per document (x-axis), and binary TREC categories
% (y-axis).
% This gave a result similar to Figure~\ref{fig:runs-rerank-median3best}.
% Unjudged documents were assumed to be irrelevant, as is common practice
% when using TREC data.
% \aht{What do you think of this almost self-referential style?}
% 
% Here we make a small alteration to the aggregation of the ME scores to
% get a single score for a document.
Rather than taking the median of all scores assigned to a document, we
take the median of scores taken from the three units that have document
orderings that have the highest agreement with the TREC orderings, or
Sormunen orderings, respectively.
In effect, the scores derived from units with high internal agreement as
computed in Section~\ref{sec:internal-agreement}, with ties broken in favor
of units with the least unjudged documents.
By aggregating scores over units that have a high agreement with the
original TREC orderings, any differences in system rankings we see should be more
attributable to the scale of the gain values, rather than perturbations in
document orderings given by different gain values.
\textcolor{red}{Note that this is a slightly less confounded methodology 
than was used in our previous paper~\cite{ME-SIGIR15}, which simply took the median 
of all units, even if the unit wildly disagreed with the ordering of documents
given by the categorical judgments. This revised methodology accounts for the 
differences between the figures and tables in this section and 
in the previous paper.}

@@

\textcolor{red}{
Generally the correlations between the system rankings based on 
categorical and ME gain values are higher when the wide judgments
are used as opposed to the narrow judgments.
This contradicts our expectations from 
Table~\ref{tab:scaling-cats}, which indicated that
a larger scale of gains led to a decrease in correlations.
This confirms that a simple argument based on the scale 
of judgments is not sufficient in explaining different system orders, 
although the number of topics used here is small (12).
We examine this further in the next section.
}

@@

\textcolor{red}{ In answering RQ\ref{item:rq2}, we have shown that
there are clear differences in system rankings using nDCG and ERR
metrics on this data when using ME scores as gain values compared with
using ordinal categories as gain values.
Depending on the judgments and the metric used, correlations between
system orderings using ME and the categorical judgments, as measured
with Kendall's $\tau$, varied between about 0.8 and -0.2. At first this
might seem like a simple scaling problem, where ME judgments are over
a wider range than categorical judgments.
However, analysis shows that simple factor cannot be the whole answer;
a much more likely explanation is that there is substantial individual
variance in not only how people perceive the relevance of an individual
document, but also in how they perceive the ratio of relevance of one
document to another.
}

### 2016-09-16 8_results_RQ4.tex
Spell check'd

>>>>

\subsection{Summary}

\textcolor{red}{ In the previous section, and in this section, we have
seen not only that relevance values for a single document vary among
users, but the ratio of relevance between two documents also varies.
Thus, in answer to RQ\ref{item:rq3}, the selection of a single gain
formulation as either a linear or exponential mapping of categorical
judgments is guaranteed to misrepresent at least half of our users in
this data set.
Similarly, choosing a single gain formulation to maximize the
statistical efficiency of system comparisons will also misrepresent a
large part of the user population.
}
